Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-01 ms.tex
Some modifications to the appendix equations.
Rescaling to new defaults.

Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
\begin{align}
  \x=\frac{1}{\zeta^2 n}\left[
    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
  \label{eq:stag_analytic}
\end{align}
where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
density profile at $r = r_{\rm s}$,

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.5 \times 10^{-3} M_{\bullet,8}^{1.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
    2.6 \times 10^{-3} M_{\bullet,8}^{1.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

@@

\begin{eqnarray}
\eddr&\approx&
  \begin{cases}
    6.6 \times 10^{-4} M_{\bullet,8}^{0.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta \Msun \, \pyear& \text{core} \\
    1.2 \times 10^{-3} \Mbheight^{0.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}

@@

An important ratio controlling the importance of thermal stability is thus
\begin{align}
\left.\frac{\dot{q}_{\rm cool}}{q v_{\rm w}^{2}/2}\right|_{\rm r{s}} \simeq
  \begin{cases}
   0.02\eta M_{\bullet,8}^{0.92}v_{500}^{-7.8}\chi^{-7.8}  &, \text{core}\\
   0.08\eta M_{\bullet,8}^{0.5}v_{500}^{-5.4}\chi^{-5.4}  &, \text{cusp},     
  \end{cases}
  \label{eq:cooling2}
\end{align}
where we have used equations (\ref{eq:rhostarrs}) and (\ref{eq:rhors}).  We thus see that we require $v_{\rm w} \gtrsim $ 300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and $M_{\bullet}$.

@@

Using equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), (\ref{eq:rhors}), (\ref{eq:cooling}), (\ref{eq:cooling2}), we can estimate the ratio of the cooling timescale to the free-fall time $\sim r/\sigma$ at the stagnation radius
\begin{align}
  \left.\frac{t_{\rm cool}}{t_{\rm ff}}\right|_{r_{\rm s}}\simeq
  \begin{cases}
    12 \Mbheight^{-0.66} \eta^{-1}(\chi v_{500})^{6.4}, & \text{core}\\
    6  \Mbheight^{-0.24} \eta^{-1}(\chi v_{500})^{4.4} ,   & \text{cusp}
  \end{cases}
  \label{eq:coolingratio}
\end{align}
We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if $\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.

{\bf BDM: in fact, I think the above criteria for tcool/tff and qdotcool/qdotwind are identical to constants of order unit, since we are using gas density estimated from free-fall time... since the BH mass dependencies are different we need to recheck algebra}

>>>>

Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
\begin{align}
  \x=\frac{1}{2 \zeta^2 n}\left[ \frac{\Mstar}{\Mbh}\left(A-n\right)+\left(B-n\right)\right],
  \label{eq:stag_analytic}
\end{align}

where $\zeta \equiv v_{w,0}/\sigma$, $n$ is the power-law slope of the
density profile at $r = r_{\rm s}$,

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.5 \times 10^{-4} M_{\bullet,8}^{1.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
    2.6 \times 10^{-4} M_{\bullet,8}^{1.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

@@

\begin{eqnarray}
\eddr&\approx&
  \begin{cases}
    6.6 \times 10^{-5} M_{\bullet,8}^{0.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta_{-1} \Msun \, \pyear& \text{core} \\
    1.2 \times 10^{-4} \Mbheight^{0.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta_{-1} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}

@@

An important ratio controlling the importance of thermal stability is thus
\begin{align}
\left.\frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rm r{s}} \simeq
  \begin{cases}
   12\eta^{-1} M_{\bullet,8}^{-0.9}v_{500}^{7.2}\chi^{7.2}  &, \text{core}\\
   4\eta^{-1} M_{\bullet,8}^{-0.5}v_{500}^{5.8}\chi^{5.8}  &, \text{cusp},     
  \end{cases}
  \label{eq:cooling2}
\end{align}
where we have used equations (\ref{eq:rhostarrs}) and
(\ref{eq:rhors}).  We thus see that we require $v_{\rm w} \gtrsim $
300 km s$^{-1}$ for stability, with a weak sensitivity on $\eta$ and
$M_{\bullet}$.  {\bf AG:I flipped the ratio to be consistent with the
  ratio of timescales given below (NB here we are comparing heating
  and cooling rates as opposed to timescales). Modulo factors of order
  unity I find no inconsistency. We should probably only keep one of
  these ratios. Note I have adopted the new convention of Gamma=0.8 is
  a cusp galaxy and Gamma=0.1 is a core galaxy.}

@@

Using equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), (\ref{eq:rhors}), (\ref{eq:cooling}), (\ref{eq:cooling2}), we can estimate the ratio of the cooling timescale to the free-fall time $\sim r/\sigma$ at the stagnation radius
\begin{align}
  \left.\frac{t_{\rm cool}}{t_{\rm ff}}\right|_{r_{\rm s}}\simeq
  \begin{cases}
    11 \Mbheight^{-0.8} \eta^{-1}(\chi v_{500})^{7.2}, & \text{core}\\
    6  \Mbheight^{-0.5} \eta^{-1}(\chi v_{500})^{5.8} ,   & \text{cusp}
  \end{cases}
  \label{eq:coolingratio}
\end{align}
We thus see that $t_{\rm cool} \lesssim 10 t_{\rm ff}$ at the
stagnation radius for low $v_{\rm w} \lesssim 250$ km s$^{-1}$ if
$\eta \sim 0.1$, but even for higher $v_{\rm w}$ if $\eta \sim 1$.
